Constant-round Blind Classical Verification of Quantum Sampling

### 2021-02-19 hamiltonian.tex
Sync Overleaf changes

For the propagation of the quantum state through the circuit, one uses the $\Hprop$ as follows:
\begin{equation*} \label{eqn:Hprop}
    \Hprop=\sum_{t=1}^T \Hprop^t,
\end{equation*}
where
\begin{equation}
    \Hprop^t=\frac{1}{2}I\otimes\proj{\widehat{t}}
    +\frac{1}{2}I\otimes\proj{\widehat{t-1}}
    -\frac{1}{2} U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
    -\frac{1}{2}U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}.
\end{equation}
Note that $\ket{\widehat{t}}\bra{\widehat{t-1}}=\ket{110}\bra{100}_{(t-1,t,t+1)}$ and similarly for $\ket{\widehat{t-1}}\bra{\widehat{t}}$.
Note that $U_t^\dagger=U_t$, since our gates are either Hadamard or Toffoli. It is observed in~\cite{PhysRevA.78.012352} that
\begin{equation}
   \Hprop^t=\frac{I}{4}\otimes(I-Z_{t-1})\otimes (I+Z_{t+1})-\frac{U_t}{4}\otimes(I-Z_{t-1})\otimes X_t\otimes (I+Z_{t+1}), \forall t=2, \ldots, T-1,
\end{equation}
and
\begin{eqnarray}
  \Hprop^1 &= & \frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1\otimes Z_2) \\
  \Hprop^T &= & \frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}\otimes X_T).
\end{eqnarray}
Combining with the fact that each $U_t$ can be written as a linear combination of terms from $\LHXZ{}$, we conclude that $\Hclock$, $\Hin$, $\Hprop$ are 6-local X-Z Hamiltonian.

@@

\begin{lem}[Lemma 1 in \cite{kempe_kitaev_regev_2006}]
    \label{thm:proj1}
    Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on Hilbert space $\cH=\cS+\cS^\bot$.
    The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
    $$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
\end{lem}

@@

\begin{lem}
    \label{lem:projection}
    Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
    $$J=\frac{8\norm{H_1}^2+ 2\norm{H_1}}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
    then we have
    $$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
\end{lem}
\begin{proof}
    Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least non zero eigenvalue of $JH_2$ is greater than $2\norm{H_1}$.
\end{proof}

>>>>

For the propagation of the quantum state through the circuit, one uses the $\Hprop$ as follows:
\begin{equation*} \label{eqn:Hprop}
    \Hprop=\sum_{t=1}^T \Hprop^t,
\end{equation*}
where
\begin{equation}
    \Hprop^t=\frac{1}{2}I\otimes\proj{\widehat{t}}
    +\frac{1}{2}I\otimes\proj{\widehat{t-1}}
    -\frac{1}{2} U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
    -\frac{1}{2}U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}.
\end{equation}
Note that $\ket{\widehat{t}}\bra{\widehat{t-1}}=\ket{110}\bra{100}_{(t-1,t,t+1)}$ and similarly for $\ket{\widehat{t-1}}\bra{\widehat{t}}$.
Note that $U_t^\dagger=U_t$, since our gates are either Hadamard or Toffoli. It is observed in~\cite{PhysRevA.78.012352} that
\begin{equation}
   \Hprop^t=\frac{I}{4}\otimes(I-Z_{t-1})\otimes (I+Z_{t+1})-\frac{U_t}{4}\otimes(I-Z_{t-1})\otimes X_t\otimes (I+Z_{t+1}), \forall t=2, \ldots, T-1,
\end{equation}
and
\begin{eqnarray}
  \Hprop^1 &= & \frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1\otimes Z_2), \\
  \Hprop^T &= & \frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}\otimes X_T).
\end{eqnarray}
Combining with the fact that each $U_t$ can be written as a linear combination of terms from $\LHXZ{}$, we conclude that $\Hclock$, $\Hin$, $\Hprop$ are 6-local X-Z Hamiltonian.

@@

\begin{lem}[Lemma 1 in \cite{kempe_kitaev_regev_2006}]
    \label{thm:proj1}
    Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on Hilbert space $\cH=\cS+\cS^\bot$.
    The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
    $$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right).$$
\end{lem}

@@

\begin{lem}
    \label{lem:projection}
    Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
    $$J=\frac{8\norm{H_1}^2+ 2\norm{H_1}}{\lambda\left(H_2\big|_{K^\bot}\right)},$$
    then we have
    $$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}.$$
\end{lem}
\begin{proof}
    Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least non zero eigenvalue of $JH_2$ is greater than $2\norm{H_1}$.
\end{proof}

### 2021-02-19 introduction.tex
Sync Overleaf changes

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks about the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations.
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non-communicating quantum provers.
In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).

@@

It is worthwhile noting that there is a simple reduction of the delegation of \emph{classical} sampling problems to decision ones: for example, the verifier can fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way. As such, classical literature of delegation of computation primarily focuses on delegation of decision problems.

Unfortunately, it is unclear about how to make this de-randomization trick work for the delegation of $\SampBQP$, 
as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.
One natural starting point is Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\BQP$. 
Indeed, some nice features of Mahadev's protocol (e.g., allowing X-Z measurements on any qubit) suggest the feasibility of generating  multi-bit measurement outcomes with the protocol. 
However, as highlighted below in the technical introduction section, there are also important drawbacks of Mahadev's protocol in its current form, which makes it hard to allow a CVQC protocol for $\SampBQP$ with desired performance. As we shall see, such difficulties do not hold for the decision problem, which demonstrates an important difference between CVQC protocols for the decision and the sampling problems.

Another desirable property of CVQC protocols is the \emph{blindness} where the prover cannot distinguish the particular computation in the protocol from another one of the same size, and hence is blind about the client's input.
Historically, blindness has been achieved in the weaker formulations of CVQC based on various techniques: e.g., the measurement-based quantum computation exploited in~\cite{BFK09}, the quantum authentication scheme exploited in~\cite{arXiv:ABOEM17}, and the self-testing technique exploited in~\cite{Nat:RUV13}.
Moreover, the blindness property is known to be helpful to establish the verifiability of CVQC protocols. However, this is never an easy task.
See for example the significant amount of efforts to add verifiability to blind computation protocol in~\cite{FK17}.
It is also known that another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe} should be helpful for establishing blindness: this is intuitive since QFHE allows fully homomorphic operations on encrypted quantum data. 
Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}.
The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's PhD thesis~\cite{mahadev_2018}.

@@

\vspace{2mm} \noindent \textbf{Techniques.} Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of (local) quantum memory in the possession of the classical verifier, or equivalently, the limited quantum power of the verifier\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time. However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the pover and discard some local qubits in the case of overflow.}. 
A precise definition is given in Section~\ref{sec:qpip_def}. 
It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only. This leads to a $\QPIP_1$ protocol for $\BQP$.
The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).

@@

The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols. In contrast to the single bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
In the context of CVQC protocols, it means that the protocol should allow the verifier to generate a desired output sample whenever the protocol accepts. 
(Of course, when the prover cheats, the verifier will reject and no further output is required in that case.)
Intuitively, the soundness requires that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interact with a malicious prover. We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in the either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.

To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems. We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined. Proving soundness of these constructions for delegating $\SampBQP$ is an interesting open question.

The requirement that the verifier needs to output a sample when accepts exposes one drawback of Mahadev's protocol: 
while it is possible, as we will show, to generate desired output samples in the Hadamard round, 
it is however unclear about how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step.

As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts. 
Our contribution is a solution to address the above two technical challenges.

@@

However, there are important differences between the cases for $\BQP$ and $\SampBQP$. Recall that the original construction of local Hamiltonian $H$ for $\BQP$ (or $\QMA$) contains two parts $H=H_{\mathrm{circuit}}+ H_{\mathrm{out}}$.
Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
Thus, the outcome of a $\BQP$ instance can be encoded by the \emph{ground energy} of $H$.

@@

The prover in the real protocol, of course, won't necessarily send copies of history states. Thus, to leverage the aforementioned intuition, one needs to avoid entanglement among these copies to obtain some sort of independence. 
We employ quantum \emph{de Finetti} theorem to address this technical challenge.
Specifically, given any permutation-invariant $k$-register state (where each register could contain many qubits), it is known that the reduced state on many subsets of $k$-register will be close to a separable state. 
Typically, for favorable error bounds, the parameter $k$ could be as large as the dimension of a single register, which is exponential in our context and hence undesirable. 
Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$. 
We can further achieve very small completeness and soundness errors in this way to satisfy the premise of Mahadev's compilation.  
Note that the established $\QPIP_1$ protocol is information-theoretically sound without any computational assumption.  (\Cref{sec:qpip1}.)

@@

Clearly from the construction, the verifier now can output a sample when it decides to accept, and output a correct sample when interacting with an honest prover (completeness). The challenge is to show that $\PiSampZ$ is computationally sound. Note that now we are in the computational setting, we cannot use quantum de Finetti theorem as above since it only holds in the information-theoretical setting. Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.

@@

It is worth comparing parallel repetition of Mahadev's protocol for $\BQP$ and $\SampBQP$. For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition. In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing round in the rest. The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine two samples learned from two Hadamard-round executions to generate one sample with much better parameters, i.e., no generic error reduction method for the sampling problem. 
In contrast, the error reduction for decision problems can be done with the majority vote. 
As a result, while the soundness error decreases exponentially for $\BQP$, as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.

@@

We apply the partition lemma iteratively to the prover's state  similarly as~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$. In particular, extra cares are required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$. To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively. Intuitively, the $\ket{\psi_0}$ component will be rejected whenever the first coordinate runs the testing round, but the verifier may be ``cheated'' to accepted incorrectly when the first coordinate runs the Hadamard round, which happens with probability $1/m$ and is where the error come from. For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate. For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate, and repeat the analysis, and so on. 
%
The intuitive analysis outlined above grosses over many technical details, and we substantiate this outline with full details in  
Section~\ref{sec:qpip0_all}.

@@

\vspace{2mm} \noindent \textbf{A generic compiler to upgrade $\QPIP_0$ protocols with blindness}. At a high-level, the idea is simple: we run the original protocol under a QFHE with the verifier's key. Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
One subtlety with this approach is due to the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.

A more subtle issue is to preserve the soundness.
In particular, compiled protocols with only one-time use of QFHE might (1) leak information about the circuit being evaluated during the homomorphic evaluation of QFHE ciphertexts (i.e., no \emph{circuit privacy});
or (2) fail to simulate original protocols upon receiving invalid ciphertexts.
We address these issues by letting the verifier switch to a fresh new key for each round of the protocol.
Details are given in \Cref{sec:BlindBQP2}.
%\XW{To KM: expand the above a bit more?}

>>>>

A complexity-theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks about the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations.
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non-communicating quantum provers.
In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of Classical Verification of Quantum Computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.,~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
On the other side, there are known complexity-theoretic limitations on the feasibility of blind CVQC in the information-theoretical setting (e.g.~\cite{aaronson_et_al:LIPIcs:2019:10582}).

@@

It is worthwhile noting that there is a simple reduction of the delegation of \emph{classical} sampling problems to decision ones: for example, the verifier can fix a seed for pseudo-randomness, send it to the prover, and then the sampling outcome can be computed  bit-by-bit under this pseudo-random seed in a deterministic way. As such, classical literature of delegation of computation primarily focuses on the delegation of decision problems. 
Unfortunately, it is unclear how to make this de-randomization trick work for the delegation of $\SampBQP$, 
as randomness in quantum computation inherently comes from quantum mechanics rather than classical probability theory. 
Thus, it seems that the delegation of $\SampBQP$ needs to take a different technical route.

The first and important step in the case of $\SampBQP$ is to identify an appropriate definition of corresponding CVQC protocols. In contrast to the single-bit $\mathrm{Accept/Reject}$ information for the decision $\BQP$, any $\SampBQP$ problem needs to always output a sample of the desired distribution.
In the context of CVQC protocols, it means that the protocol should allow the verifier to generate the desired output sample whenever the protocol accepts. Of course, when the prover cheats, the verifier will reject and no further output is required in that case.  
Intuitively, the soundness should require that the verifier $V$ should never be ``cheated'' to accept and output an incorrect sample even when interacting with a malicious prover.

A natural attempt is to directly apply Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} for $\SampBQP$.  Note that Mahadev's protocol consists of the so-called testing round, where the prover's behavior is tested,  and the Hadamard round, where measurement outcomes are generated. 
Indeed, some nice features of the Hadamard round,  e.g., allowing X-Z measurements on any qubit,  suggest the feasibility of generating  multi-bit measurement outcomes with the protocol. 
However, the requirement that the verifier needs to output a sample whenever accepting also exposes one drawback of Mahadev's protocol: while it is possible, as we will show, to generate desired output samples in the Hadamard round, 
it is however unclear how to generate such a sample when the protocol accepts in the testing round, since the sampling information stored in the quantum state will be disturbed by the testing step. 
Note that this difficulty is essentially due to the different requirements between the definitions of CVQC protocols for the decision and the sampling problems.

Another desirable property of CVQC protocols is the \emph{blindness} where the prover cannot distinguish the particular computation in the protocol from another one of the same size, and hence is blind about the client's input.
Historically, blindness has been achieved in the weaker formulations of CVQC based on various techniques: e.g., the measurement-based quantum computation exploited in~\cite{BFK09}, the quantum authentication scheme exploited in~\cite{arXiv:ABOEM17}, and the self-testing technique exploited in~\cite{Nat:RUV13}.
Moreover, the blindness property is known to be helpful to establish the verifiability of CVQC protocols. However, this is never an easy task.
See for example the significant amount of effort to add verifiability to blind computation protocol in~\cite{FK17}.
It is also known that another important primitive called the Quantum Fully Homomorphic Encryption (QFHE)~\cite{BJ15, DSS16, LC18, NS18, OTF18, mahadev_qfhe} should be helpful for establishing blindness: this is intuitive since QFHE allows fully homomorphic operations on encrypted quantum data. 
Indeed, in another paper~\cite{mahadev_qfhe}, Mahadev constructed the first leveled QFHE based on similar techniques and computational assumptions from~\cite{FOCS:Mahadev18a}.
The constructed QFHE automatically implies a blind CVQC protocol, however, without verifiability.
Extending this protocol with verifiability seems challenging as hinted by failed attempts in Section 2.2.2 of Mahadev's Ph.D. thesis~\cite{mahadev_2018}.

@@

\vspace{2mm} \noindent \textbf{Techniques.} Let us revisit Mahadev's CVQC protocol~\cite{FOCS:Mahadev18a} first for some technical background. 
Following~\cite{FOCS:Mahadev18a}, we formally define $\QPIP_{\tau}$ as classes of CVQC protocols where $\tau$ refers to the size of (local) quantum memory in the possession of the classical verifier, or equivalently, the limited quantum power of the verifier\footnote{Intuitively, the size of local quantum memory limits the size of qubits that a general (entangled) quantum operation can be operated on at the same time. However, the verifier is still able to operate on all the qubits in a streaming fashion: i.e., receive the qubits sent from the prover and discard some local qubits in the case of overflow.}. 
A precise definition is given in Section~\ref{sec:qpip_def}. 
It is known that $\BQP$ can be efficiently verified by a classical verifier that can perform a single qubit $X$ or $Z$ measurement~\cite{PhysRevA.93.022326, mf16}, by reducing any $\BQP$ problem to a local Hamiltonian problem where each term consists of  $X$ and $Z$ only. This leads to a $\QPIP_1$ protocol for $\BQP$.
The main contribution of Mahadev~\cite{FOCS:Mahadev18a} can hence be deemed as a way to compile this $\QPIP_1$ protocol into a $\QPIP_0$ protocol (i.e., with a fully classical verifier).

@@

As we mentioned earlier that an appropriate definition of CVQC for $\SampBQP$ is needed to capture the intuition that the verifier should always output the desired sample whenever accepts, but should never be "cheated" to accept and output an incorrect sample when interacting with a malicious prover. We formalize this by a strong \emph{simulation-based} definition (Section~\ref{sec:samp_definition}), where we require that the joint distribution of the decision bit $d \in \set{\Acc, \Rej}$ and the output $z$ (which is $\bot$ when $d = \Rej$) is $\eps$-close (in  either statistical or computational sense) to an ``ideal distribution'' $(d,z_{ideal})$, where $z_{ideal}$ is sampled from $D_x$ when $d = \Acc$ and set to $\bot$ when $d = \Rej$.

To the best of our knowledge, we are the first to formally define the delegation of quantum sampling problems. We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be naturally generalized to delegate quantum sampling problems and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the simulation-based soundness property we defined. Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question.

The requirement that the verifier needs to output a sample when accepts makes a direct application of Mahadev's protocol infeasible for $\SampBQP$. As a result, in order to construct a $\QPIP_0$ protocol for $\SampBQP$,  one needs to (1) construct a $\QPIP_1$ protocol for $\SampBQP$ with very small completeness and soundness errors, and (2) amend Mahadev's construction so that the protocol will generate the desired sample whenever it accepts. 
Our contribution is a solution to address the above two technical challenges.

@@

However, there are important differences between the cases for $\BQP$ and $\SampBQP$. Recall that the original construction of local Hamiltonian $H$ for $\BQP$ (or $\QMA$) contains two parts $H=H_{\mathrm{circuit}}+ H_{\mathrm{out}}$.
Roughly speaking, $H_{\mathrm{circuit}}$ helps guarantee its ground space only contains \emph{valid} history states with the correct input and circuit evolution, while $H_{\mathrm{out}}$'s energy encodes the 0/1 output for $\BQP$ circuits.
Thus, the outcome of a $\BQP$ instance can be encoded by the \emph{ground energy} of $H$.

@@

The prover in the real protocol, of course, won't necessarily send copies of history states. Thus, to leverage the aforementioned intuition, one needs to avoid entanglement among these copies to obtain some sort of independence. 
We employ the quantum \emph{de Finetti} theorem to address this technical challenge.
Specifically, given any permutation-invariant $k$-register state (where each register could contain many qubits), it is known that the reduced state on many subsets of $k$-register will be close to a separable state. 
Typically, for favorable error bounds, the parameter $k$ could be as large as the dimension of a single register, which is exponential in our context and hence undesirable. 
Fortunately, since there is no entangled operation in the protocol to perform on two copies of history states, one can employ an efficient variant of the quantum \emph{de Finetti} theorem~\cite{Brandao2017} whose error bound depends poly-logarithmically on the dimension of the register, which leads to an efficient $\QPIP_1$ protocol for $\SampBQP$. 
We can further achieve very small completeness and soundness errors in this way to satisfy the premise of Mahadev's compilation.  
Note that the established $\QPIP_1$ protocol is information-theoretically sound without any computational assumption.  (\Cref{sec:qpip1}.)

@@

Clearly from the construction, the verifier now can output a sample when it decides to accept, and output a correct sample when interacting with an honest prover (completeness). The challenge is to show that $\PiSampZ$ is computationally sound. Note that now we are in the computational setting, we cannot use the quantum de Finetti theorem as above since it only holds in the information-theoretical setting. Furthermore, parallel repetition for computationally sound protocols are typically difficult to analyze, and known to not always work for protocols with four or more messages~\cite{BIN97,PW12}.

@@

It is worth comparing the parallel repetition of Mahadev's protocol for $\BQP$ and $\SampBQP$. For $\BQP$, the verifier simply chooses to run the Hadamard and testing rounds independently for each repetition. In contrast, our $\PiSampZ$ runs the Hadamard round in one repetition and run the testing round in the rest. The reason is that in $\SampBQP$, as well as generically in sampling problems, there is no known approach to combine two samples learned from two Hadamard-round executions to generate one sample with much better parameters, i.e., no generic error reduction method for the sampling problem. 
In contrast, the error reduction for decision problems can be done with the majority vote. 
As a result, while the soundness error decreases exponentially for $\BQP$, as we see below (and also in the above $\QPIP_1$ protocols), for $\SampBQP$, $m$-fold repetition only decreases the error to $\poly(1/m)$.

@@

We apply the partition lemma iteratively to the prover's state  similarly to~\cite{arXiv:ChiaChungYam19}, but with significant differences to show the soundness of $\PiSampZ$ for $\SampBQP$. In particular, extra care is required to reason about the computational indistinguishability of the verifier's output sample from the correct distribution $D_x$. To gain some intuition, let us apply the partition lemma to the prover's state $\ket{\psi}$ with respect to the first coordinate, which decompose $\ket{\psi} = \ket{\psi_0} + \ket{\psi_1}$ with $\ket{\psi_0} \in S_0$ and  $\ket{\psi_1} \in S_1$, respectively. Intuitively, the $\ket{\psi_0}$ component will be rejected whenever the first coordinate runs the testing round, but the verifier may be ``cheated'' to accepted incorrectly when the first coordinate runs the Hadamard round, which happens with probability $1/m$ and is where the error come from. For the $\ket{\psi_1}$ component, $V$ will produce a sound output if it runs the Hadamard round at the first coordinate. For the case that $V$ chooses to run the testing round at the first coordinate, we can analyze it by further applying the partition lemma to $\ket{\psi_1}$ with respect to the second coordinate, and repeat the analysis, and so on. 
%
The intuitive analysis outlined above grosses over many technical details, and we substantiate this outline with full details in  
Section~\ref{sec:qpip0_all}.

@@

\vspace{2mm} \noindent \textbf{A generic compiler to upgrade $\QPIP_0$ protocols with blindness}. At a high-level, the idea is simple: we run the original protocol under a QFHE with the verifier's key. Intuitively, this allows the prover to compute his next message under encryption without learning the underlying verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
One subtlety with this approach is the fact that the verifier is classical while the QFHE cipher text could depend on both quantum and classical data.
In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical, which is fortunately satisfied by~\cite{mahadev_qfhe}.

A more subtle issue is to preserve the soundness.
In particular, compiled protocols with a single application of QFHE might (1) leak information about the circuit evaluated by the verifier through its outputted QFHE ciphertexts (i.e., no \emph{circuit privacy});
or (2) fail to simulate original protocols upon receiving invalid ciphertexts from the prover.
We address these issues by letting the verifier switch to a fresh new key for each round of the protocol. 
Details are given in \Cref{sec:BlindBQP2}.
%\XW{To KM: expand the above a bit more?}

### 2021-02-19 model.tex
Sync Overleaf changes

In this section, we formally introduce the task of delegation for quantum sampling problems. We start by recalling the complexity class $\SampBQP$ defined by Aaronson~\cite{aaronson_2013, aaronson_arkhipov_2011}, which captures the class of sampling problems that
are approximately solvable by polynomial-time quantum algorithms.

@@

Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$, instead of the stringent requirement of outputting a perfect sample. There are multiple reasons for allowing an inverse polynomial error. For example, conceivable physical realizations of quantum computer may consist of inherent noise. We refer the readers to~\cite{aaronson_2013, aaronson_arkhipov_2011} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.

>>>>

In this section, we formally introduce the task of delegation for quantum sampling problems. We start by recalling the complexity class $\SampBQP$ defined by Aaronson~\cite{aaronson_2013, Boson}, which captures the class of sampling problems that
are approximately solvable by polynomial-time quantum algorithms.

@@

Note that in the above definition, there is an accuracy parameter $\eps$ and the quantum sampling algorithm only requires to output a sample that is $\eps$-close to the correct distribution in time $\poly(n,1/\eps)$, instead of the stringent requirement of outputting a perfect sample. There are multiple reasons for allowing an inverse polynomial error. For example, conceivable physical realizations of quantum computer may consist of inherent noise. We refer the readers to~\cite{aaronson_2013, Boson} for the discussion therein on why this better captures the sampling problem solvable by realistic quantum computers.
